Adopting agile in the large: motivations, success factors and challenges

### 2014-05-13 journal/article.tex
Work in progress

>>>>

"C: Difficulties in long term planning"

[P5]
Even though we believed we had built a reasonable release plan, the team lacked
confidence in our ability to achieve the release objectives.
As a result, we met with the business owners to inform them  they  needed to
either remove the constraint of minimal credible requirements or change the
target date.  In negotiating with the business owners, we were able to shift the
date by adding two additional iterations to the release.

Comment:
There had been a demand for a particular feature set for the release, set by business owners

[P6]
removing governance gates where processes were overly bureaucratic, and changing
the way we conducted resource planning and portfolio management.

Comment:
Talking about removing "broader systemic impediments" with pilot teams

[P9]
While the significance of this success was widely profiled within the company,
there were still issues to resolve.  The team had increased their adeptness at
short term execution, but there were big gaps in long term planning. This gap
was later addressed by applying a more advanced Scrum technique of 116multilevel
planning [7]. Focus group lunches were initiated for the business unit’s Scrum
Masters to share stories and issues.

Comment:
The success of one particular team's transformation

[P10]
The  need  for  improved release planning was also behind the second innovation
made at this time arising from ideas encountered at the conference.  The  team
had been struggling to balance the need for longer term planning (multiple
product release over a 3-18 month period) with the scrum discipline of sprint
planning (a tight 2-4 week focus) – but without re-introducing  a static
schedule-driven approach that would undermine the agile dynamic.

[P10]
VELOCITY  VACUUM:  Despite best intentions, establishing a measurable team
velocity over time remained a huge challenge,  undermining  our efforts at
release planning.  At the sprint level, the team struggled to embrace the idea
of recording actual  effort  remaining rather than simply proportionally burning
down from their original task estimates.  Shifting priorities, fractional  or
virtual  participation on multiple sprint teams, quirky tools, and the 
management of ‘off-sprint’ tasks all made it very difficult to perceive actual
team velocity. When it came to release planning, the team was naturally hesitant
to estimate against product backlog items when it had such a limited grasp of
actual performance at the task level.

[P13]
Part of the release framework included the creation of a few key milestones.  
In our self-organizing, agile environment we were very sensitive to imposing
heavy milestones on our teams.  However, we still believed that there were key
milestones that would align our teams to our on-time, high quality release
objectives while enhancing the agility of our teams.

[P26]
One of the management concerns when transitioning to agile was the conflict
between long-term and short-term planning. One of the threats seen was that
backlogs and agile planning would give us only short-term visibility.
We had many experienced program managers, who were able to estimate the size and
duration of new programs based on their earlier experiences, and we saw no
reason to leave that experience unutilized. Thus we decided to keep those both:
long-term vision based on experience, and short-term “strategy” based on
backlogs. This has resulted in more time spent on actual planning but also in
improvement in the plans themselves.

[P31]
We needed to find a way to make the requirements definition and product
roadmapping process more Agile.  To help facilitate a solution, we brought in
Enthiosys, a management consulting firm with deep expertise in Agile project
management. Enthiosys helped us create and implement a system that would bring
together development, marketing, product management and even representatives
from sales and support each quarter to scope out a living roadmap of features
for a product.

[P38]
Another tension is trying to produce reasonable initial estimates. The estimates
assist the business side with macrolevel prioritization of which products to
invest in. One of the elements we worked hard to develop in the teams is
learning as we build instead of trying to gather all of the requirements and do
big design up front.
This is often problematic because the time when the estimates are required is
also when the teams know the least about the product. They have only begun to
learn about the solution. Of course the teams do their best to leverage
similarities with other products, especially as many of them have similar
elements given the publishing domain, but this does not completely resolve the
issue and it continues to be an area to improve.
The transformation has gone a long way toward developing and increasing the
trust between the business and technology, thus helping the business feel more
confident in when products will be delivered. For example, one team previously
went through three rounds of high/macro-level estimation and refinement before
being given the green light. On the next project the team was able to learn from
the previous project and what the business was looking for in terms of packaging
and presentation of the high level estimates. The result was the next project
required only one round of estimation. Another result was that the project was
broken up into more phases.
The first project had been done in two large phases. In the first phase the
majority of the features were completed and the second was the more or less for
overflow.
In the second project, the project was broken up into four phases and the
business only budgeted out the first two phases.
The team also focused on a smaller set of requirements and had a clearer idea of
what was to be built. The second two phases were unfunded and were less defined.
This allowed the development team to do less guessing while allowing the
business to risk less by investing. Then after the first release and into the
second they could refine and plan the other two phases and allow them to
leverage feedback from the user base to determine whether further investment was
warranted.
